Self-Supervised Transfer Learning From 2D Images to 3D Point Clouds

### 2022-05-09 doc/paper.tex
adds some relevant works

\begin{itemize}
    \item Demonstrates that previous work in 3D \cite{xie2020pointcontrast} works by learning to extrapolate 3D scenes. When purely learning improved features on fully-overlapping regions the performance gain disapears.
    \item Provide a 2D feature extractor and pre-training algorithm. Demonstrate that these features can improve 2D segmentation.
    \item Transfer learned 2D features onto a 3D model
\end{itemize}

@@

\textbf{Sparse 3D convolutions.} Talk about submanifold networks, Minkowski Engine, etc

\textbf{Contrastive Learning.} Talk about SimCLR, BOYL, etc. Then talk about PointContrast.

\textbf{Knowledge Distilation} Need to read up on this

>>>>

\begin{itemize}
    \item Demonstrates that previous work in 3D \cite{xie2020pointcontrast} works by learning to extrapolate 3D scenes. When purely learning improved features on fully-overlapping regions the performance gain disappears.
    \item Provide a 2D feature extractor and pre-training algorithm. Demonstrate that these features can improve 2D segmentation.
    \item Transfer learned 2D features onto a 3D model
\end{itemize}

@@

\textbf{Sparse 3D convolutions.} Talk about submanifold networks, Minkowski Engine \cite{choy20194d}, pointnet \cite{charles2017PointNet} PointNet++ \cite{qi2017pointnet++}.

\textbf{Downstream tasks.} PointGroup \cite{}

\textbf{Contrastive Learning.} Talk about SimCLR \cite{chen_simple_2020}, BOYL \cite{grill_bootstrap_nodate}, Moco \cite{he_momentum_2020}. Then talk about PointContrast. \cite{choy2019Fully}

\textbf{Contrastive learning variations}
Supervised contrastive losses \cite{khosla_supervised_2021} Guided contrastive learning in 3D \cite{jiang2021Guided}. Prototypical learning \cite{li_prototypical_2021}

\textbf{Contrastive Learning in 3D}
DepthContrast \cite{zhang2021Self}

\textbf{Using 2D images.} 3D-sis \cite{hou20193d}, Using 2D images to learn 3D segmentation \cite{genova2021learning} \cite{frey_continual_2021}. 3dmv \cite{angela2018joint}

Closest to my work: \cite{yunze2020p4contrast}. Their approach is to augment 3D points with features from 2D images and use their combined multi-modal features as the output of their model. They require however that their model always have access to 2D images and cannot operate on solely colorized point clouds at runtime.
